\Title

### 2021-01-12 manuscript/manuscript.tex
Replace flowchart for an algorithm (#91)
Remove the flowchart image for illustrating the process for estimating the best prediction for synthetic data.
Replace it with an algorithm instead.

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
This process is carried out on both ground and airborne synthetic surveys.
See Figure~\ref{fig:flowchart} for a graphical illustration of it.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
    \caption{
        Flowchart for comparing the performance of the source distributions.
        For each source distribution we propose different values for its
        parameters (see Tables~\ref{tab:parameters-ground-survey}
        and~\ref{tab:parameters-airborne-survey}).
        These values are then combined to obtain several set of parameters
        which are iteratively submitted to the process illustrated on this
        figure.
        Finally we obtain the best prediction generated by each source
        distribution as the one that achieves the best score.
    }
    \label{fig:flowchart}
\end{figure}

>>>>

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
This process is carried out on both ground and airborne synthetic surveys.
See Algorithm~\ref{alg:source_distributions_comparison} for a concise
representation of it.

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}

  define possible values for each parameter
  \;

  generate each possible combination of parameters values: obtain several
  \emph{sets of parameters}
  \;

  \For{each set of parameters}{

    select the $M$ locations of the equivalent sources
    \;

    estimate the source coefficients
    \;

    predict field values on target grid points
    \;

    calculate the RMS between the predictions and the target grid
    \;
  }

  the best set of parameters produces the smallest RMS
  \;

  \BlankLine
  \setstretch{1}
  \caption{Algorithm for estimating the best prediction using synthetic data.}
  \label{alg:source_distributions_comparison}
\end{algorithm}
